Sustainable Pathways for Irish homes in changing TIMES

### 2021-07-19 manuscript.tex
Figure for Results - almost finished

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{pgf-pie}
\usepackage{pgfplots}
\usepackage{calc}
\usepackage{graphicx}
\usepackage{float}
\usepackage{anyfontsize}
\usepackage{pgfplots}
\usepackage{comment}
\usepackage{booktabs}
\usepackage{rotating}
\usepackage{siunitx}
\usepackage{eurosym}
\usepackage{multirow}
\usepackage{xcolor} 
\usepackage{colortbl}

@@

The advantage of energy sytem model is to oberve the intersectoral impacts for further insights...
\begin{figure}[!htbp]
 \centering
 \includegraphics[width=\textwidth]{Figures/SectorCost.png}
 \caption{Heat Pump by type per scenario}
 \label{fig:SectorCost}
\end{figure}

>>>>

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{pgf-pie}
\usepackage{pgfplots}
\usepackage{calc}
\usepackage{graphicx}
\usepackage{float}
\usepackage{anyfontsize}
\usepackage{pgfplots}
\usepackage{comment}
\usepackage{booktabs}
\usepackage{rotating}
\usepackage{siunitx}
\usepackage{eurosym}
\usepackage{multirow}
\usepackage{xcolor} 
\usepackage{colortbl}
\usepackage{subcaption}

@@

The advantage of an energy system model is to observe the intersectoral connections. Figure \ref{fig:SectorFuel} presents a boxplot of the 2030 fuel consumption in four different sectors, under the four scenarios which comply with the 51 \% reduction.....
\begin{figure}[!htbp]
 \centering
 \includegraphics[width=\textwidth]{Figures/SectorFuel.png}
 \caption{Sector Fuel per scenario}
 \label{fig:SectorFuel}
\end{figure}

for further insights...

\begin{figure}[!htbp]
 \centering
 \includegraphics[width=\textwidth]{Figures/SectorCost.png}
 \caption{Sector Cost per scenario}
 \label{fig:SectorCost}
\end{figure}
